Diffusive Homeostasis in a Self-Organizing Recurrent Neural Network \\ \begin{large} Spatially dependent Interaction as a Determinant of Neural Activity and Plasticity \end{large}

### 2017-03-06 draft.tex
.

\includegraphics[width=\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_sim_vs_mat.png}

@@

\caption{Comparison of distribution of standard deviation (A) and skewness (B) for random-matrix solutions (gray) and values acquired from simulation (blue), Neumann boundaries. Same simulation data as in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} was used, each point representing a single simulation. The histograms for the analytic solutions were generated for 50 $\rm D$ values, spanning equally between $\rm D=0 mu m^2 /ms$ and $\rm D=20 mu m^2 /ms$. Each column is a histogram of $\rm 200$ firing-rate solutions for randomly generated positions, giving a total of $\rm 10000$ matrix solutions.}

>>>>

\includegraphics[width=0.7\textwidth]{../../plots/firing_rate_dists/fir_rate_dist_sim_vs_mat.png}

@@

\caption{Comparison of distribution of standard deviation (A) and skewness (B) for random-matrix solutions (gray) and values acquired from simulation (blue), Neumann boundaries. Same simulation data as in Figure \ref{Fir_Rate_Dist_Width_Skewness_vs_D} was used, each point representing a single simulation. The histograms for the analytic solutions were generated for 50 $\rm D$ values, spanning equally between $\rm D=0 mu m^2 /ms$ and $\rm D=20 \mu m^2 /ms$. Each column is a histogram of $\rm 200$ firing-rate solutions for randomly generated positions, giving a total of $\rm 10000$ matrix solutions.}
